### 2019-06-15 2-Chapters/1-Chapter/chapter1.tex
SO HARD

% The opposite: decentralized broadcasting, and the age of IoT
Finally, a third kind of systems are of the opposite kind, and can be designed as decentralized broadcasting: an antenna is still in charge of many devices, but such devices can only send up-link packets, and the only down-link data they can receive are short acknowledgements sent from the base-station to indicate success or failure of an up-link packet.
This family of wireless systems are referred to as Internet of Things,
and a typical example of application is for sensor networks.
For the future development of smart grids, smart cities, smart homes, or smart agriculture, sensor networks are promised to be widely deployed.
Two examples of future applications that are already in deployment, in France or other countries, are connected buildings and connected agriculture.
For buildings, the main goal is to reduce the cost of heating empty buildings and use temperature sensor networks to get accurate and regular data about the temperature in each room and each floor, and let the centralized heat control optimize its cost and energy consumption.
For agriculture, one example can be to equipped every cow (in large farms) with a sensors that emits biological information, such as body temperature or stress level etc, in order to optimize the time of milking and monitors the health of the animals.

@@

- les télécoms ? télécoms décentralisées ?
  => okay
- l'IoT c'est quoi ?
- les bandits c'est quoi ?
- les bandits multi-joueurs, pourquoi ?
- pourquoi étudier ça ?
- OK qu'est ce qu'on a proposé et pourquoi ?
  => plan des contributions, bullet point (1ère version, je pourrai faire mieux après)

@@

>>>>

% The opposite: decentralized broadcasting, and the age of IoT
Finally, a third kind of systems are of the opposite kind, and can be designed as decentralized broadcasting: an antenna is still in charge of many devices, but such devices can only send up-link packets, and the only down-link data they can receive are short acknowledgements sent from the base-station to indicate success or failure of an up-link packet.
This family of wireless systems are referred to as Internet of Things,
and a typical example of application is for sensor networks.

For the future development of smart grids, smart cities, smart homes, or smart agriculture, sensor networks are promised to be widely deployed.
Two examples of future applications that are already in deployment, in France or other countries, are connected buildings and connected agriculture.
For buildings, the main goal is to reduce the cost of heating empty buildings and use temperature sensor networks to get accurate and regular data about the temperature in each room and each floor, and let the centralized heat control optimize its cost and energy consumption.
For agriculture, one example can be to equipped every cow (in large farms) with a sensors that emits biological information, such as body temperature or stress level etc, in order to optimize the time of milking and monitors the health of the animals.

This third kind of wireless systems are characterized by their decentralized nature: due to the really limited information that the base station can send to the devices, it is no longer possible to optimize the efficiency of the network from the centralized point-of-view of the base station.
In the present and future IoT networks, many devices of heterogenous nature are using the same antenna for many different applications.
A common hypothesis is that such IoT devices have a strong constraint on their power consumption, as most of them will be deployed without a direct power access and will use a battery, which duration should be maximized (typically more than 10 years).
Another common constraint for IoT devices is their low duty cycle, as most applications target one to a few messages sent by day, in strike opposition to the high data-rate pursued for centralized systems such as 4G/5G and WiFi.
%
In this thesis, we study Internet of Things networks, and these two constraints of low power consumption (or long battery life) and low duty cycle are essential.

\paragraph{Cognitive Radio.}
%

@@

- contexte historique technologique => okay

- les télécoms ? télécoms décentralisées ? => okay

- l'IoT c'est quoi ? exemple d'applications ? => okay ?

- les bandits c'est quoi ?

- les bandits multi-joueurs décentralisés, pourquoi ?

- pourquoi étudier ça ?

- OK qu'est ce qu'on a proposé et pourquoi ? => plan des contributions, bullet point (1ère version, je pourrai faire mieux après)

@@

\TODOL{Tous les paragraphes suivants sont copiés collés de plus tard dans la thèse, je peux les réadapter ici, et les supprimer/raccourcir plus loin}
